---
title: "Q1 trial"
author: "Leslie Long Nu"
date: '2022-06-26'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# import libraries

```{r library}
packages = c('tidyverse', 'ggplot2', 'lubridate', 'treemap', 'plotly', 
             'rPackedBar', 'zoo')
for (p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p,character.only = T)
}
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

# import raw data

```{r import raw data, eval=FALSE}
pubs <- read_csv('rawdata/Pubs.csv')
restaurants <- read_csv('rawdata/Restaurants.csv')
travel <- read_csv('rawdata/TravelJournal.csv')
```

# derive revenue for pubs and restaurants
The following code chunk extracts travel records related to restaurants and pubs using `filter()` and derives spending of each visit using `inner_join()` and `mutate()`.

```{r revenue, eval=FALSE}
restaurantstr <- travel %>%
  filter(purpose == 'Eating') %>% 
  mutate(travelTime = travelEndTime - travelStartTime) %>%
  select(-c(travelStartTime:travelEndTime, endingBalance)) %>%
  inner_join(y= restaurants, 
            by = c('travelEndLocationId'= 'restaurantId')) %>%
  mutate(visitDuration = checkOutTime - checkInTime) %>%
  select(-c(purpose, location, checkOutTime)) %>%
  rename('restaurantId' = 'travelEndLocationId',
         'spending' = 'foodCost')
  

pubstr <- travel %>%
  filter(purpose == 'Recreation (Social Gathering)') %>%
  mutate(travelTime = travelEndTime - travelStartTime) %>%
  select(-c(travelStartTime: travelEndTime, endingBalance)) %>%
  inner_join(y= pubs, 
             by = c('travelEndLocationId'= 'pubId')) %>%
  mutate(visitDuration = checkOutTime - checkInTime,
         spending = as.numeric(visitDuration/60)* hourlyCost) %>%
  select(-c(purpose, location, checkOutTime)) %>%
  rename('pubId' = 'travelEndLocationId')
```

# save as rds

```{r eval=FALSE}
saveRDS(restaurantstr, 'rawdata/restaurants.rds')
saveRDS(pubstr, 'rawdata/pubs.rds')
```


# read data

```{r read data}
#checkin <- read_csv('rawdata/CheckinJournal.csv')
#travel <- read_csv('rawdata/TravelJournal.csv')
pubs <- readRDS('rawdata/pubs.rds')
restaurants <- readRDS('rawdata/restaurants.rds')
```

# data wrangling 

```{r pub& restaurant}
restaurants$hourlyCost <- NA
restaurants$locationType <- 'Restaurant'
pubs$locationType <- 'Pub'
restaurants <- rename(restaurants, locationId = restaurantId)
pubs <- rename(pubs, locationId= pubId)
restaurants$locationId <- paste('Restaurant', restaurants$locationId)
pubs$locationId <- paste('Pub', pubs$locationId)
all <- rbind(restaurants, pubs)
```

```{r}
all <- all %>%
  mutate(weekday = wday(checkInTime, label= TRUE),
         date = date(checkInTime))

pubs <- all %>%
  filter(locationType == 'Pub')

restaurants <- all %>%
  filter(locationType == 'Restaurant')
```


# prepare data for weekday visualization

```{r weekday plot}
# visit records by weekday 
all_wday <- all %>%
  group_by(locationId, weekday) %>%
  summarise(visits = n(),
            revenue = sum(spending),
            locationType = first(locationType))

restaurant_wday <- all %>%
  group_by(locationId, weekday) %>%
  summarise(visits = n(),
            revenue = sum(spending),
            locationType = locationType)
# filter = locationId & location type
```

# save rds for weekday visualization

```{r save rds}
saveRDS(all, 'data/all.rds')
saveRDS(all_wday, 'data/all_wday.rds')
saveRDS(restaurants, 'data/restaurants.rds')
saveRDS(pubs, 'data/pubs.rds')
```

```{r}
lvl = c('Mon', 'Tue', 'Wed', 'Thu', 'Fri', 'Sat', 'Sun')

all1 <- all %>%
  group_by(locationType, locationId, date) %>%
  summarise(visits= n(),
            weekday = first(weekday)) %>%
  ungroup() 

all_mean <- all1 %>%
  group_by(locationId, weekday) %>%
  summarise(meanv = mean(visits)) %>%
  ungroup()

all1 %>%
  filter(locationType == 'restaurant' &
               locationId == 447) %>%
  ggplot(aes(x= date,
             y = visits)) +
  geom_line() +
  geom_hline(data = all_mean %>%
               filter(locationId==447),
             aes(yintercept = meanv),
             linetype= 'dashed',
             size = .4) +
  facet_grid(~ factor(weekday, levels = lvl)) +
  theme_bw()
  
```

```{r}
#sort(unique(all[all$locationType=='restaurant', locationId]))
```

# prepare data for packed bar visualization

```{r packed bar data}
all_monthly <- all %>%
  mutate(`Month Year` = as.yearmon(date)) %>%
  group_by(locationType, locationId, `Month Year`) %>%
  summarise(Revenue= sum(spending))
```

```{r}
all_monthly$`Month Year`
```

# save rds for packed bar visualization

```{r save all_monthly}
saveRDS(all_monthly, 'data/all_monthly.rds')
```

```{r}
max(all_monthly$mon)
```

```{r packed bar}

all_mon <- all_monthly %>%
  filter(mon== 'May 2022' &
         locationType=='Restaurant')

p <- plotly_packed_bar(input_data = all_mon , 
                       label_column = 'locationId',
                       value_column = 'Revenue',
                       #number_rows = 20,
                       plot_title = 'Monthly Revenue in Descending Order in May 2022', 
                       xaxis_label = 'Monthly Revenue',
                       hover_label = 'Monthly Revenue',
                       min_label_width = 0.001,
                       color_bar_color = '#ffa500',
                       label_color = 'white') 

p <- p %>%
      layout(
        xaxis= list(
          ticktext = list('0', '$10K', '$20K', '$30K', '$40K', '$50K')
        )
      )
    p
#plotly::config(p1, displayModeBar = FALSE)
```


```{r line2 }
ggplot(data= all_monthly %>% filter(locationId==442),
  aes(x= mon, y = Revenue)) +
  geom_line()
```

